---
title: "Challenge 2 - Testing New Forecasting Algorithms"
author: "Marco Zanotti"
date: ""
output: 
  rmdformats::downcute:
    highlight: tango
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(timetk)
```

## Content

This challenge is about testing previously unseen time series forecasting
algorithms.  

The purpose of this challenge is to test your ability to use new models 
for time series forecasting as soon as they become available.  



## Requirements

You are required to produce a fully reproducible notebook report explaining 
all the steps to forecast with Bayesian models & GAMs.  

You can use the feature sets we created during Lecture 2.  

References:  
- [Bayes Models](https://albertoalmuinha.github.io/bayesmodels/)  
- [GAMs](https://hsbadr.github.io/additive/)  
- [GAMs method](https://petolau.github.io/Analyzing-double-seasonal-time-series-with-GAM-in-R/)  



## Data

You have to apply the new methodologies to the same dataset we used 
throughout the Lectures.

```{r data, echo=FALSE}
artifacts_list <- read_rds("../artifacts/feature_engineering_artifacts_list.rds")
data_prep_tbl <- artifacts_list$data$data_prep_tbl
forecast_tbl <- artifacts_list$data$forecast_tbl

splits <- time_series_split(
  data_prep_tbl, 
  date_var = optin_time,
  assess = "8 weeks", 
  cumulative = TRUE
)
splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(optin_time, optins_trans)
```

