---
title: "Challenge 4 - Testing Forecasting Algorithms"
author: "Marco Zanotti"
date: ""
output: 
  rmdformats::downcute:
    highlight: tango
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(timetk)
```

## Content

This challenge is about testing time series forecasting algorithms 
(Lectures 4, 5, 6, 7, 8 and 10).  

The purpose of this challenge is to test your ability to use many models
to forecast different time series and to evaluate them.  



## Requirements

You are required to produce a fully reproducible notebook report explaining 
all the steps to forecast with Time Series, Machine Learning and Ensemble models.  

You are free to apply the feature sets you created during challenge 1.  



## Data

Challenge dataset contains:  
- daily website page views   
- hourly website organic searches  
- weekly website sales  

```{r data, echo=FALSE}
data <- read_rds("../data/challenges_dataset.rds")
data %>% 
  map(~ select(., 1:2)) %>% 
  map(~ pivot_longer(., -date, names_to = "series")) %>% 
  bind_rows() %>% 
  plot_time_series(.date_var = date, .value = value, .facet_vars = series, .facet_scales = "free")
```
