---
title: "Challenge 1 - Feature Engineering"
author: "Marco Zanotti"
date: ""
output: 
  rmdformats::downcute:
    highlight: tango
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(timetk)
```

## Content

This challenge is all about explorative data analysis (EDA) and
features engineering in time series (Lectures 1 and 2).  

The purpose of this challenge is to test your ability to effectively understand 
the dynamics of different time series allowing you to create one or more 
features' recipe.  

The analysis you perform at this first stage will be the basis to perform accurate
forecasts during the next challenges.  



## Requirements

You are required to produce a fully reproducible notebook report explaining 
all the steps that takes you towards the creation of all the new features 
you would like to use in forecasting models.  

At least one feature set for each time series has to be produced.  



## Data

Challenge dataset contains:  
- daily website page views   
- hourly website organic searches  
- weekly website sales  

```{r data, echo=FALSE}
data <- read_rds("../data/challenges_dataset.rds")
data %>% 
  map(~ select(., 1:2)) %>% 
  map(~ pivot_longer(., -date, names_to = "series")) %>% 
  bind_rows() %>% 
  plot_time_series(.date_var = date, .value = value, .facet_vars = series, .facet_scales = "free")
```

