---
title: "Challenge 0 - Jumpstart"
author: "Marco Zanotti"
date: ""
output:
  rmdformats::downcute:
    highlight: tango
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(timetk)
```

## Content

This challenge is about time series forecasting.  

The purpose of this challenge is to apply the methods you know by now 
to produce the most accurate forecast for a single time series.



## Requirements

You are required to produce a fully reproducible notebook report explaining 
all the steps to forecast and their evaluation.    

You have to apply your methods on the train set, forecast 8 weeks ahead and 
evaluate on the test set.  

You have to evaluate your methods with RMSE.   

You have to produce the results in 30 minutes.  

You are free to apply any method and software you like (even MS Excel).  



## Data

Challenge dataset contains:  
- daily time series of website subscribers volume (in log)

```{r data, echo=FALSE, message=FALSE}
data <- read_csv("../data/challenge0_dataset.csv")
plot_time_series(data, .date_var = date, .value = value, .color_var = type, .smooth = FALSE)
```
