---
title: "Challenge (Optional) - Modeltime"
author: "Marco Zanotti"
date: "2021-2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(timetk)
```

## Content

This is challenge is about the use of modeltime R package (Lecture 3).  

The purpose of this challenge is to apply the modeltime workflow to one or
more time series of the challenge.   



## Requirements

You are required to produce a fully reproducible notebook report explaining 
all the steps to forecast with Prophet, Random Forest and SVM algorithms.  

You are free to apply the feature sets you created during challenge 1.  



## Data

Challenge dataset contains:  
- daily website page views   
- hourly website organic searches  
- weekly website sales  

```{r data, echo=FALSE}
data <- read_rds("../data/challenges_dataset.rds")
data %>% 
  map(~ select(., 1:2)) %>% 
  map(~ pivot_longer(., -date, names_to = "series")) %>% 
  bind_rows() %>% 
  plot_time_series(.date_var = date, .value = value, .facet_vars = series, .facet_scales = "free")
```
